Titeln på avhandlingens språk

### 2023-02-11 body/part1/overview/methodology.tex
more writing

@@

\medskip
In the following subsections we will discuss two illustrative use-cases for our methodology; \acl{WCA} and \acl{NCS} research and benchmarking.
\Cref{summary:methodology:usecase_wca} discusses the application of our methodology to \gls{WCA}.
This work was originally published in \cref{paper:olguinmunoz2018demoscaling,paper:olguinmunoz2019edgedroid}.
Next, in \cref{summary:methodology:usecase_ncs} we expand this discussion to \glspl{NCS}, a discussion originally approached in \cref{paper:olguinmunoz2022cleave}.

\subsection{Use case: \acl{WCA}}\label{summary:methodology:usecase_wca}

@@

\todo[inline]{Move part of this to the ``tools'' section?}
The implementation of the client-side emulation necessary for our methodology follows in these works a trace-based design.
\Cref{fig:methodology:wca:conceptual} presents a diagram of our conceptual approach to this implementation.
We introduce a tool, \emph{EdgeDroid \num{1.0}}, which replays a pre-recorded trace of sensory inputs to the original \gls{WCA} backend.
The tool is implemented in Android, allowing for its easy deployment on the same kind of \gls{COTS} mobile and/or wearable devices (e.g.\ Google Glass~\cite{googleglass}) on which real \gls{WCA} applications are intended to run in the future.
Furthermore, this tool is instrumented, allowing us to collected a multitude of system-level metrics at runtime which can then be analyzed.
On the other hand, the trace in question corresponds to a pre-recorded sequence of sensory inputs obtained from a real execution of the \gls{WCA} by a human volunteer.
The trace is recorded in a near-ideal setting, such that it does not include either human mistakes or segments with degraded system responsiveness.
Once recorded, the trace is manually segmented into the logical component steps of the task, and these are replayed in sequence back to the backend by the EdgeDroid tool.

@@

The final advantage corresponds to extensibility.
As long as the tasks belong to the same category of \gls{WCA} applications (in this case, step-based cognitive assistance), using a trace makes extending the tool to different tasks merely a matter of recording a new trace.
\todo[inline]{}

@@

\subsection{Use case: \acsp{NCS}}\label{summary:methodology:usecase_ncs}

\todo[inline]{Discuss, at high level, the advantages ofthis methodology for NCSs.
Refer back to related work. }

\subsection{Tools for the application of the methodology}

\todo[inline]{Here we actually present the tools}

\subsubsection{\acs{WCA}: EdgeDroid}

\subsubsection{\acsp{NCS}: CLEAVE}

\subsubsection{ExPECA Testbed \& the Ainur software stack}

>>>>

This thesis presents a comprehensive study on latency-sensitive applications in Edge Computing.
The primary contribution of this research is a methodology for analyzing and evaluating the performance of these applications.
The methodology is validated through the examination of two initial case studies, \gls{WCA} and \glspl{NCS}.
In addition to the methodology, this thesis includes several other key contributions.
A prototype testbed and accompanying software framework have been developed to provide a platform for conducting experiments in Edge Computing.
Furthermore, a further deeper exploration into the \gls{WCA} case studied yielded the first-ever model of human behavior in \gls{WCA}, which is a significant advancement in the field.
The methodology, the case studies, and the prototype testbed provide valuable insights into the performance of latency-sensitive applications in Edge Computing and can be used as a basis for future research in this area.

@@

\medskip
In the following subsections we will discuss two illustrative case studies for our methodology; \acl{WCA} and \acl{NCS} research and benchmarking.
\Cref{summary:methodology:usecase_wca} discusses the application of our methodology to \gls{WCA}.
This work was originally published in \cref{paper:olguinmunoz2018demoscaling,paper:olguinmunoz2019edgedroid}.
Next, in \cref{summary:methodology:usecase_ncs} we expand this discussion to \glspl{NCS}, a discussion originally approached in \cref{paper:olguinmunoz2022cleave}.

\subsection{Case study: \acl{WCA}}\label{summary:methodology:usecase_wca}

@@

The implementation of the client-side emulation necessary for our methodology follows in these works a trace-based design.
\Cref{fig:methodology:wca:conceptual} presents a diagram of our conceptual approach to this implementation.
We introduce a tool, \emph{EdgeDroid \num{1.0}}, which replays a pre-recorded trace of sensory inputs to the original \gls{WCA} backend.
The tool is implemented in Android, allowing for its easy deployment on the same kind of \gls{COTS} mobile and/or wearable devices (e.g.\ Google Glass~\cite{googleglass}) on which real \gls{WCA} applications are intended to run in the future.
Furthermore, this tool is instrumented, allowing us to collected a multitude of system-level metrics at runtime which can then be analyzed.
On the other hand, the trace in question corresponds to a pre-recorded sequence of sensory inputs obtained from a real execution of the \gls{WCA} by a human volunteer.
The trace is recorded in a near-ideal setting, such that it does not include either human mistakes or segments with degraded system responsiveness.
Once recorded, the trace is manually segmented into the logical component steps of the task, and these are replayed in sequence back to the backend by the EdgeDroid tool.

@@

The final advantage corresponds to extensibility.
As long as the tasks belong to the same category of \gls{WCA} applications (in this case, step-based cognitive assistance), using a trace makes extending the tool to different tasks merely a matter of recording a new trace.

@@

\subsection{Case study: \acsp{NCS}}\label{summary:methodology:usecase_ncs}

\todo[inline]{Discuss, at high level, the advantages of this methodology for NCSs.
Refer back to related work. }

\subsection{ExPECA Testbed \& the Ainur software stack}
